\bf On semidefinite-representable sets over valuation fields

### 2024-11-11 article/paper_padic_spec.tex
tentative title abstract

\title{\bf Title}

@@

\begin{abstract}
\end{abstract}

@@

\subsection{Context and motivations}

%Il faudra entre autre mentionner (et peut être motiver l'approche p-adique) :
%\begin{itemize}
%\item les questions ouvertes de complexité concernant la programmation semidefinie (pas clair si NP $\cap$ co-NP
%  dans le modele de Turing)
%\item les questions ouvertes géométriques (Conjecture de Lax)
%\end{itemize}

\subsection{Main results}

\newpage
\section{Preliminaries}

@@

\begin{definition}
  We call a matrix $M \in \allmat_{d,d}(K)$ \emph{positive semidefinite} (in symbols $M \succeq 0$)
  if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.
  We denote by $\allmat_{d,d}^+(K) \subset \allmat_{d,d}(K)$ the set of positive semidefinite matrices.
  The characteristic polynomial of a matrix $M \in \allmat_{d,d}(K)$ is denoted $\chi_M \in K[T]$.
\end{definition}

>>>>

%\title{\bf Title}
%\title{\bf On polyhedra and spectrahedra over valuation fields}
\title{\bf On semidefinite-representable sets over valuation fields}

@@

\begin{abstract}
  \noindent
  Real polyhedra and real spectrahedra are respectively the feasible sets of linear programming
  (LP) and semidefinite programming (SDP). This paper investigates versions of these sets and of
  the related optimization problems with data over a field $K$ with valuation.
  We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
  representable over $K$ but are not $K$-spectrahedra.
\end{abstract}

@@

%\subsection{Context and motivations}
%Il faudra entre autre mentionner (et peut être motiver l'approche p-adique) :
%\begin{itemize}
%\item les questions ouvertes de complexité concernant la programmation semidefinie (pas clair si NP $\cap$ co-NP
%  dans le modele de Turing)
%\item les questions ouvertes géométriques (Conjecture de Lax)
%\end{itemize}
%\subsection{Main results}

%\newpage
\section{Preliminaries}

@@

\begin{definition}
  We say that a matrix $M \in \allmat_{d,d}(K)$ is \emph{positive semidefinite} (in symbols $M \succeq 0$)
  if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.
  We denote by $\allmat_{d,d}^+(K) \subset \allmat_{d,d}(K)$ the set of positive semidefinite matrices.
  The characteristic polynomial of a matrix $M \in \allmat_{d,d}(K)$ is denoted $\chi_M \in K[T]$.
\end{definition}
